Stability concerns in random matrices

### 2018-03-25 random_matrix_stability.Rmd
Another paragraph of results

We examined the stability of 100 million random communities in which $S = [2, 15]$ before and after the addition of variatince in $\gamma_{i}$.

>>>>

We examined the stability of 100 million random communities in which $S$ ranged between 2-15 before and after the addition of variation in $\gamma_{i}$. Elements of $\boldsymbol{A}$ were selected from a random uniform distribution $\mathcal{U}\left(-4, 4\right)$, and variation in \gamma_{i} was generated with a random uniform distribution of $\mathcal{U}\left(1, 1000\right)$ (see Supporting Information S1). Random communities were categorised in one of four ways (Table 1): (1) Unstable before and after the addition of variance in $\gamma_{i}$ (unstable), (2) stable before and after the addition of variance in $\gamma_{i}$ (stable), (3) unstable before but not after the addition of variation in $\gamma_{i}$ (stabilised), and (4) stable before but not after the addition of variation in $\gamma_{i}$ (destabilised; Table 1).

As $S$ increases, so does the effect of variation in $\gamma_{i}$ on increasing system stability (Figure 1). At high $S$, nearly all stable communities were only stable due to the effect of variation in $\gamma_{i}$, which rarely destabilised species rich communities (Supporting Information S1). All else being equal, variation in generation time therefore becomes more influential in stabilising random communities as community size increases, meaning that variation in generation time might be an important contributor to stability in large communities.
